%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\chapter{Specialty/Species}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Human}

\featentry{Tretonin }{[Jaffa]}
\descfeat
{You now receive regular doses of tretonin from the SGC, and need no longer rely upon a symbiote to survive.}
{Prerequisites: The Symbiote feat.}
{You must take regular does of tretonin to survive. If you go without a tretonin dose for longer than 24 hours, you must make one Fortitude save per hour (DC 10 + 2 per hour he has gone without the tretonin). If you fail one of these saves, your vitality points are immediately reduced to 0 and you lose 1 wound point at the end of each time interval lasting a number of minutes equal to your Constitution, until you are given a does of tretonin or you die.

You automatically gain 7 days’ worth of tretonin at the start of any mission. This does not count against your gear picks or any bundles assigned to the mission. While operating within the confines of the SGC, you are assumed to receive doses of tertonin automatically}
{When the Tretonin feat is taken, the Symbiote feat immediately vanishes and you lose all the benefits and drawbacks thereof. It may not be taken again.

You cannot have both the Tretonin feat and the Symbiote feat at the same time under any circumstances. A character with a symbiote who takes tretonin gains no benefits from the drug.

In timeline terms, this feat may only be taken after the Season Six episode The Changeling (GM’s discretion).}

New Gear
Tertonin
Tretonin is a new drug, developed by the SGC from the Pangarans. It effectively serves as a replacement immune system, freeing the Jaffa who takes it from his dependence upon a symbiote. One dose must be taken every 24 hours for it to function.

Medical Supplies	 Picks  	PR	RI	Duration	Qualities	Weight
Tretonin	1 per 2 doses	—	—	—	—	—
