%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Valkyrie}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

The Valkyries are the elite combat units of the Asgard and are regarded as great warriors among humankind. Despite their frail build and slight frame, the Valkyries are swift and capable combatants that specialize in analyzing and then overwhelming their enemies. Valkyries use the Asgard's advanced technologies to gain an edge over opponents; they study their enemies' movements, apply mathematical theories and statistical analyses to battle tactics, and formulate plans to overcome their natural physiological handicaps through the application of intelligence and force. They know their weapons (and the technology that powers them) intimately and are able to apply this knowledge in practical situations in order to take their opponents down quickly and efficiently.

\columnbreak

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace{1.5cm}\textbf{Species:}] Asgard
\item[\hspace{1.5cm}\textbf{Character Level:}] 5+
\item[\hspace{1.5cm}\textbf{Intelligence:}] 13+
\item[\hspace{1.5cm}\textbf{Base Attack Bonus:}] +5
\item[\hspace{1.5cm}\textbf{Knowledge (Tactics):}] 8+ ranks
\item[\hspace{1.5cm}\textbf{Sense Motive:}] 4+ ranks
\item[\hspace{1.5cm}\textbf{Feats:}] Far Shot, Goa'uld Hunter, Perfect Stance
\end{description*}

\textbf{Abilities:} Intelligence and Dexterity are the most important abilities to the Valkyrie. The Valkyrie's philosophy revolves around the application of scientific theory and statistical probability to combat, making Intelligence key to their tactics. They also make extensive use of the shock spear and other ranged weapons, making Dexterity essential during combat.

\textbf{Vitality:} d10

\end{multicols}

\setlength{\intextsep}{-2cm}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Bluff & Cha\\
Bureaucracy & Cha\\
Computers & Int\\
Concentration & Wis\\
Craft & Int\\
Cultures & Wis\\
Demolitions & Int\\
First Aid & Int\\
Hide & Dex\\
Intimidate & Str/Cha\\
Listen & Wis\\
Move Silently & Dex\\
Pilot & Dex\\
Profession & Wis\\
Search & Int\\
Sense Motive & Wis\\
Sleight of Hand & Dex\\
Spot & Wis\\
Survival & Wis\\


\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 6 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\setlength{\intextsep}{14.0pt plus 4.0pt minus 4.0pt}

\vspace*{2cm}

\vspace*{\fill}

\begin{center}
\textsc{\Large}\\[0.25cm]
\rule{\linewidth}{0.5mm}\\[0.6cm]
\fontsize{30}{30} \selectfont Season 1 pg. 133\\
\rule{\linewidth}{0.5mm}\\[0.6cm]
\vfill
\end{center}

\pagebreak



