%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Explorer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

Since the Stargate has offered bold adventurers and daring academics a chance to venture beyond the limits of our solar system, the explorer has epitomized both of these archetypes - those who contribute to understanding alien technology and those who explore worlds beyond the gate. A team without an explorer may find itself baffled by the puzzles and quirks of alien technologies and cultures.

\columnbreak

\textbf{Abilities:} Most explorers fancy a bit of rough and tumble, and decent Strength and Dexterity can be very helpful.The most pressing ability for any explorer, however, is unquestionably Intelligence, the source of wits he stakes his life upon during every mission.

\textbf{Vitality:} d10

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Boating & Dex\\
Climb & Str\\
Cryptography & Int\\
Cultures & Wis\\
Driver & Dex\\
First Aid & Wis\\
Gather Information & Cha\\
Handle Animal & Cha\\
Jump & Str\\
Knowledge & Int\\
Languages & Int\\
Listen & Wis\\
Mechanics & Int\\
Open Locks & Dex\\
Search & Int\\
Spot & Wis\\
Survival & Wis\\
Swim & Str\\
Tumble & Dex\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 6 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\modebab{}
\modefor{}
\goodref{}
\modewil{}
\modedefb{}
\goodinit{}
\poorgear{}
\poorres{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, All Over the World, Direction Sense +2, Obsessive \textsuperscript{*}}
\leveltwo{Bookworm (1/2)}
\levelthree{Bonus Feat}
\levelfour{Direction Sense +3, Uncanny Dodge (Dex bonus)}
\levelfive{Bonus Feat}
\levelsix{All Over the World (Advanced)}
\levelseven{Bonus Feat}
\leveleight{Direction Sense +4, Uncanny Dodge (Can't be Flanked)}
\levelnine{Bonus Feat, Danger Sense (Melee)}
\levelten{Rugged (+2)}
\leveleleven{Bonus Feat, Bookworm (1/4)}
\leveltwelve{All Over the World (Grand), Direction Sense +5, Uncanny Dodge (Traps +1)}
\levelthirteen{Bonus Feat}
\levelfourteen{Lifeline}
\levelfifteen{Bonus Feat, Danger Sense (Ranged)}
\levelsixteen{Direction Sense +6, Uncanny Dodge (Traps +2)}
\levelseventeen{Bonus Feat}
\leveleighteen{All Over the World (Perfect)}
\levelnineteen{Bonus Feat, Bookworm (1/10)}
\leveltwenty{Direction Sense +7, Rugged (+4), Uncanny Dodge (Traps +3)}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The explorer begins play with the following feats:

Armor Group Proficiency (Light)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Pistol)

\textbf{Obsessive:} The explorer makes his way through determination and the occasional flash of brilliance. Whenever the explorer spends 1 or more action dice to increase an Intelligence-based skill check, his threat range with that skill check is increased by 1/4 his class level (rounded up).

\vspace*{5pt}
\tagline{\textbf{This is the explorer's core ability.}}

\textbf{All Over the World:} Even after joining the SGC, the explorer never ceases to wander the globe, honing his skills and nosing around in new places. At 1st level, he gains the World Traveler feat.

At 6th level, the explorer gains the Advanced Skill Mastery feat for the World Traveler feat.

At 12th level, the explorer gains the Grand Skill Mastery feat for the World Traveler feat.

At 18th level, the explorer gains the Perfect Skill Mastery feat for the World Traveler feat.

All prerequisites for these feats - including minimum skill ranks and character level - are waived.

\textbf{Direction Sense:} At 1st level, the explorer gains a +2 competence bonus with all skill checks made to navigate from place to place, regardless of the skill being used. Further, he does not need to spend an action die to convert a threat to a critical success when making navigation checks. These bonuses also apply when navigating through space. This bonus increases by an additional +1 at 4th level and for every 4 class levels gained thereafter.

\textbf{Bookworm:} The explorer has unparalleled research skills and can frequently just walk up to the right part of any library or flip open a book to the right page with spooky accuracy. Starting at 2nd level, the explorer may reduce the amount of time required to conduct any research- whether using books, a computer, or other means. This ability only affects researches that would otherwise take 5 minutes or longer.

At 2nd level, this ability reduces the research time required to 1/2 standard (rounded up).

At 11th level, this ability reduces the research time required to 1/4 standard (rounded up).

Finally, at 19th level, this ability reduces the research time required to 1/10 standard (rounded up).

\textbf{Bonus Feat:} At 3rd level and for every other class level gained thereafter, the explorer gains 1 bonus basic combat or basic skill feat. He must meet all prerequisites for this feat before choosing it.

\textbf{Uncanny Dodge:} Starting at 4th level, the explorer gains the ability to react to danger before his senses would typically permit him to become aware of it. He retains his Dexterity bonus to Defense (if any) when flat-footed or being attacked by an invisible adversary (though he still loses his Dexterity bonus to Defense when immobilized).

At 8th level, the explorer may react to opponents on alI sides as easily as he can to one attacker, and may therefore no longer be flanked. This ability denies scouts and others with the sneak attack ability the opportunity to use flank condition to sneak attack the explorer unless the attacker is at least 4 character levels higher than the explorer.

At 12th level, the explorer gains an intuitive sense that grants him a +1 competence bonus with Reflex saves made to avoid traps and a +1 competence bonus to Defense against attacks from traps.

These two bonuses increase to +2 at 16th level and to +3 at 20th level.

A character who gains the uncanny dodge ability from two or more classes may combine his class levels from all such classes in a limited fashion to determine this ability's effectiveness. The character's class levels in each class are rounded down to the nearest multiple of 4 and then added together to determine the character's uncanny dodge abilities.

Example: A 9th-level explorer/7th-level Prime possesses the uncanny dodge benefits of a 12th-level character (8class levels from the 9th-level explorer and 4 class levels from the 7th-level explorer).

\textbf{Danger Sense:} At 9th level, the explorer may use his keen wits to avoid harm. So long as he is no more than lightly encumbered and either wearing no armor or light armor, the explorer may add his lntelligence modifier to his Dexterity modifier when determining his Defense against melee and unarmed attacks.

At 15th level, this bonus extends to attacks with hurled weapons, firearms, and all other ranged attacks.

This bonus is lost any time the explorer is denied his Dexterity modifier to Defense.

\textbf{Rugged:} At 10th level, the explorer's Constitution score rises by 2.

At 20th level, the explorer's Constitution score rises by an additional 2 (for a total rise of 4).

\textbf{Lifeline:} At 14th level, the explorer's fortune reaches a zenith and he may slip out of even the most shocking circumstances (largely) unscathed. Whenever the explorer has 1 or more vitality points remaining and suffers enough damage to lower his vitality below 0, he suffers only enough damage to lower his vitality to 0.

Likewise, whenever the explorer has 1 or more wound points remaining and suffers enough damage to lower his wounds below 0, he suffers only enough damage to lower his wounds to 0. All excess damage is ignored.

This ability is applied every time the explorer suffers at least 1 point of damage (after armor, damage reduction, and other damage-reducing abilities are applied), regardless of the source of damage. The explorer's lifeline ability affects damage from attacks, falls, poison, and all other sources of injury.