%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Guardian}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

After centuries of service to the System Lords, the Jaffa have developed a unique warrior class, prepared to fight to the death for their Goa'uld masters. With the rebellion of some of these warriors, the SGC has discovered a new source of rugged combatant recruits. While the guardian fulfills many of the same functions as the soldier, this character's fighting style relies more on the legendary hardiness and resilience of the Jaffa/symbiote fusion. A team without a guardian lacks his near fanatical commitment to the cause, and his experience with Goa'uld technology.

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace{1.5cm}\textbf{Species:}] Jaffa. This class is typically restricted to Jaffa characters, though an inventive player may convince his GM that his character concept warrants another species being trained in the class.
\end{description*}

\textbf{Abilities:} Like the soldier, the guardian prizes all the physical abilities - Strength, Dexterity, and Constitution.

\textbf{Vitality:} d12

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Climb & Dex\\
Concentration & Wis\\
Craft & Int\\
Escape Artist & Dex\\
First Aid & Dex\\
Hide & Dex\\
Intimidate & Str/Cha\\
Jump & Dex\\
Move Silently & Dex\\
Pilot & Dex\\
Sport & Str/Dex\\
Spot & Dex\\
Survival & Dex\\
Tumble & Dex\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 4 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\goodbab{}
\goodfor{}
\poorref{}
\goodwil{}
\gooddefb{}
\poorinit{}
\poorgear{}
\moderes{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Enforcer (Basic), Unbreakable \textsuperscript{*}}
\leveltwo{Soak 1/Session}
\levelthree{Toughness}
\levelfour{Bonus Feat}
\levelfive{Accelerated Healing}
\levelsix{Enforcer (Advanced)}
\levelseven{Toughness}
\leveleight{Bonus Feat}
\levelnine{Accelerated Healing, Superior Metabolism (No Damage with Save)}
\levelten{Superior Conditioning}
\leveleleven{Soak 2/Session, Toughness}
\leveltwelve{Bonus Feat, Enforcer (Grand)}
\levelthirteen{Accelerated Healing}
\levelfourteen{Soul of War}
\levelfifteen{Superior Metabolism (1/2 Damage with Failed Save),Toughness}
\levelsixteen{Bonus Feat}
\levelseventeen{Accelerated Healing}
\leveleighteen{Enforcer (Perfect)}
\levelnineteen{Soak 3/Session, Toughness}
\leveltwenty{Bonus Feat, Superior Conditioning}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The Guardian begins play with the following feats:

Armor Group Proficiency (Light)

Armor Group Proficiency (Medium)

Armor Group Proficiency (Heavy)

Weapon Group Proficiency (Hurled)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Handgun)

Weapon Group Proficiency (Rifle)

\textbf{Unbreakable:} The guardian may spend 1 action die to ignore any and all morale penalties for a number of minutes equal to ·the highest face on his current action dice type (for example, spending 1d6 in this fashion grants immunity for 6 minutes).
Further, the guardian may spend his action dice to increase the result of any saving throw to resist fear made by an ally or teammate within verbal or visual contact.

\vspace*{5pt}
\tagline{\textbf{This is the \currentclassname's core ability.}}

\textbf{Enforcer:} The guardians have long served the Goa'uld as enforcers, controlling occupied worlds through fear and oppression. At 1sst level, the guardian gains a virtual basic skill feat called "Enforcer." This feat grants a + 2 bonus with Concentration and Intimidation checks, and increases the guardian's threat range with these skiIIs to 19-20.

At 6th level, the guardian gains the Advanced Skill Mastery feat for his Enforcer feat.

At 12th level, the guardian gains the Grand Skill Mastery feat for his Enforcer feat.

Finally, at 18th level, the guardian gains the Perfect Skill Mastery feat for his Enforcer feat.

All prerequisites for these feats - including minimum character level - are waived.

\textbf{Soak:} Beginning at 2nd level, once per session as a free action, the guardian may gain a number of points of damage reduction equal to his base attack bonus until the start of his initiative count during the following round. These points follow all the standard rules for damage reduction, and stack with points of damage reduction gained from armor, other class abilities, and other character options.

The guardian may use this ability up to twice per session at 11th level and up to three times per session at 19th level. This ability may not be used more than once during any one round.

lf the guardian also possesses this ability from levels gained with another class (such as Prime), the number of uses per session stack, but the ability may still not be used more than once during any one round.

\textbf{Toughness:} At 3rd level and for every 4 class levels gained thereafter, the guardian gains the Toughness feat.

\textbf{Bonus Feat:} At 4th level, the guardian gains 1 bonus feat from any combat tree (basic, melee, ranged, or unarmed). He must meet alI prerequisites for this feat before choosing it.
At 8th level and for every 4 class levels gained thereafter, the guardian gains 1 additional bonus combat feat , with the same restrictions.

\textbf{Accelerated Healing:} The guardian recovers from minor injuries at a truly start!ing rate. Beginning at 5th level, he recovers 1 point of vitality every ten minutes (100 rounds), regardless of his level of exertion. Further, the guardian also recovers 2 wounds per day of rest (instead of 1, as standard).

At 9th level, the guardian recovers 1 point of vitality every 5 minutes (50 rounds), and recovers 3 wounds per day of rest.

At 13th level, the guardian recovers 1 point of vitality every 2 minutes (20 rounds), and recovers 4 wounds per day of rest.

At 17th level, the guardian recovers 1 point of vitality every minute (10 rounds), and recovers 5 wounds per day of rest.

The guardian does not benefit from this ability while his wound points are below 0.

\textbf{Superior Metabolism:} Beginning at 9th level, whenever the guardian succeeds with a Fortitude save to suffer reduced damage from any effect (such as poison), he instead suffers no damage.

Starting at 15th level, whenever the guardian fails with a Fortitude save to suffer reduced damage from any effect (such as poison), he suffers only ½ damage (rounded down).

\textbf{Superior Conditioning:} Guardians train with a ferocity and dedication that has terrified the System Lords' lesser servants for millennia. At 10th level, the guardian chooses two of his three physical abilities (Strength, Dexterity, or Constitution). Each of the two chosen abilities rises by 1. The guardian may not choose the same ability twice.
At 20th level, the guardian once again chooses two of his three physical abilities, each of which rises by 1. The guardian may choose the same two abilities he chose at 10th level. Once again, the guardian may not choose the same ability twice.

Example: At 10th level, Mad'rak chooses Strength and Dexterity, each of which rises by 1. When he achieves 20th level, he chooses Strength and Constitution, each of which rises by an additional 1. Mad'rak's Strength was increased by a total of 2 by this ability, while his Dexterity and Constitution were each raised by 1.

\textbf{Soul of War:} With high-tech weapons, ancient blades, and even his bare hands, the guardian is a whirlwind of violence. Beginning at 14th level, once per round after the guardian takes his standard action(s), he may make 1 single attack as a free action. This attack occurs in addition to any other attacks or actions the guardian makes during the same round. This ability may be used a number of times per session equal to the guardian's class level.


