%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Pointman}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

SG teams are by nature small and tightly coordinated self-reliant squads. To maximize their efficiency, the SGC often as.signs a pointman. either as a team leader or coordinator to bring out the best in all of the team's members. Pointmen train with many skills, and often enhance or assist their fellow teammates. They're also the most flexible characters available. A team that lacks a pointman may have trouble becoming more than the sum of its parts.

\columnbreak

\textbf{Abilities:} No ability is most important for pointmen, but Charisma and Wisdom come close. These abilities form the basis for most of their pre-set class skills, and are most often used when interacting with other people-something good pointmen do a lot.

\textbf{Vitality:} d10

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Bluff & Cha\\
Bureaucracy & Cha\\
Craft & Int\\
Diplomacy & Cha\\
Driver & Dex\\
First Aid & Wis\\
Knowledge & Int\\
Profession & Wis\\
Sense Moptive & Wis\\
Sport & Str/Dex\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 6 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\modebab{}
\modefor{}
\moderef{}
\goodwil{}
\poordefb{}
\poorinit{}
\goodgear{}
\moderes{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Generous \textsuperscript{*}, Versatility (6 Skills)}
\leveltwo{Assistance (1/2)}
\levelthree{Lead 1/Session, Versatility (7 Skills)}
\levelfour{Tactics 1/Session}
\levelfive{Lead 2/Session}
\levelsix{Cross-Class Ability, Versatility (8 Skills)}
\levelseven{Lead 3/Session}
\leveleight{Tactics 2/Session (+2 bonus)}
\levelnine{Cross-Class Ability, Lead 4/Session, Versatility (9 Skills)}
\levelten{Serendipity 1/Session}
\leveleleven{Assistance (1/4), Lead 5/Session}
\leveltwelve{Tactics 3/Session, Versatility (10 Skills)}
\levelthirteen{Lead 6/Session}
\levelfourteen{Strategy 1/Session}
\levelfifteen{Cross-Class Ability, Lead 7/Session, Versatility (11 Skills)}
\levelsixteen{Tactics 4/Session (+3 bonus)}
\levelseventeen{Lead 8/Session}
\leveleighteen{Cross-Class Ability, Versatility (12 Skills)}
\levelnineteen{Assistance (1/10), Lead 9/Session}
\leveltwenty{Serendipity 2/Session, Tactics 5/Session}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The Pointman begins play with the following feats:

Armor Group Proficiency (Light)

Armor Group Proficiency (Medium)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Handgun)

Weapon Group Proficiency (Rifle)

\textbf{Generous:} A pointman may spend (and roll) action dice to increase the rolls of teammates and allies within verbal or visual contact just as if increasing his own rolls, so long as he's within line of sight or can speak directly to them throughout their action (radio communication is acceptable). When this ability is used, the pointman's class abilities, modifiers, and other character options that affect action die use supersede those of the target.

Example: If a pointman's target possesses an ability that typically allows him to spend 1 action die to roll 2 in a situation in which the pointman is spending 1 or more action dice to increase 1 of the target's rolls, then only 1 action die is rolled per action die spent. The target's ability is ignored, as only the pointman's abilities relating to action die use are applied when he spends and rolls action dice to increase a teammate's or ally's roll.

Also, when the pointman and target character disagree about how 1 or more action dice granted by this ability should be spent the pointman's decision is final. The target character cannot overrule the pointman concerning how the pointman's action dice are applied.

\vspace*{5pt}
\tagline{\textbf{This is the \currentclassname's core ability.}}

\textbf{Versatility:} At 1st level, a pointman may choose 6 cross-class skills to become class skills for him.

At 3rd level and for every 3 class levels gained thereafter, the pointman may choose 1 additional cross-class skill to become a class skill for him.

Finally, when the pointman uses his versatility class ability to turn Hobby into a class skill for him, then all Hobby focuses are considered to be class skills for him.

\textbf{Assistance:} Starting at 2nd level, the pointman may choose to assist one teammate within verbal or visual contact. The amount of time it takes this teammate to use one of his class abilities or skills is reduced as follows.

At 2nd level, the pointman's assistance reduces the time required to 1/2 standard (rounded up).

At 11th level, the pointman's assistance reduces the time required to 1/4 standard (rounded up).

Finally, at 19th level, the point man's assistance reduces the time required to 1/10 standard (rounded up).

The pointman's assistance only affects activities that would otherwise take 1 hour or longer.

\textbf{Lead:} Starting at 3rd level, once per session, any or all of the pointman's teammates within his line of sight may use his result from one skill check for one action they're performing as a group, such as climbing, sneaking, or setting explosives.

Example: A team is sneaking past some sleepy guards, and its pointman uses this ability. Only the pointman must make a Move Silently check, using his skill bonus. If the pointman succeeds, then the entire team succeeds, but if he fails, the entire team fails.

This ability may not be used in conjunction with any check prompted by a species feat.

At 5th level, and for every 2 class levels gained thereafter, the pointman may use this ability one additional time per session.

\textbf{Tactics:} At 4th level, once per session as a free action, the pointman may issue an order to a number of teammates or allies equal to his Charisma modifier +1 (minimum 1). This order must be specific, such as "Cover Sam while she gets the door open!" as opposed to "Help Sam!" While the pointman's teammates or allies carry out this order, they gain a +1 morale bonus with all skill checks made to carry out the order (at the GM's discretion). The pointman may be one of the characters targeted to benefit from this ability. If the pointman is the only character benefiting from this ability, he need not speak in order to advise himself.

At 8th level, this bonus increases to +2, and at 16th level, this bonus increases to +3.

Finally, at 8th level and for every 4 class levels gained thereafter, the pointman may use this ability one additional time per session.

If the pointman also possesses this ability from levels gained with another class (such as officer), the number of uses per session stack, but the abiIity's effects do not stack- the pointman applies only the highest bonus gained from any one class to all uses of this ability.

\textbf{Cross-Class Ability:} At 6th level, the pointman gains one ability from one base class listed below. An ability followed by text such as “1/session, 2/session" may be taken multiple times, gaining the improvements listed after each comma with each successive "upgrade."

At 9th level, and for every 3 class levels gained thereafter, the pointman gains one additional cross-class ability, also from the following list.

Explorer: All over the world; bonus basic combat or basic skill feat x1, x.2; bookworm (½), direction sense +2 ,+3; uncanny dodge (Dex bonus).

\begin{description*}
\item[\hspace{1.5cm}Guardian\textsuperscript{*}:] Accelerated healing (1 vitality per 10 minutes, 2 wounds per day); bonus combat feat; Enforcer(Basic); soak 1/session; Toughness.
\item[\hspace{1.5cm}Scientist:] Improvise +2, +3; learned; Ph.D. (1 skill);research.
\item[\hspace{1.5cm}Scout:] Bushmaster x1, x2; rough living +2; sneak attack+1d6; stalker.
\item[\hspace{1.5cm}Soldier:] Bonus combat feat x1; x2, x3; damage reduction 1/-; armor use +1
\item[]\textsuperscript{*}This cross-class ability is only available if the pointman is a Jaffa, or with the GM's permission.
\end{description*}

\textbf{Serendipity:} At 10th level, once per session, an item, person, lucky break, or bout of inspiration comes to the team's rescue, just when they need it most. During times of crisis, the GM may, without a prompt from the pointman, introduce an element to help the team. Some examples are a contact (with information equal to that gained from a successful education check with a DC of 20 or less), a hint (as if the pointman had succeeded with an inspiration check against a DC of 20 or less), a piece of gear (with a gear pick cost equal to 1/2 the pointman's class level or less, rounded down, an alien device (with an RP cost equal to 1/3, the pointman's class level or less, rounded down), or a successful skill check (even if the pointman didn't make one).

Regardless of the effect, this ability implies sudden and unexpected fortune, and the GM should strive to keep his serendipitous assistance fresh and inventive. The pointman may ask for his lucky break at any time, though the GM may refuse by offering the pointman 2 action dice instead, This ability is considered to have been used if the pointman accepts the dice, and the pointman does not earn XP for gaining these action dice.

At 20th level, the GM may introduce up to two lucky breaks per session.

\textbf{Strategy:} Beginning at 14th level, once per session as a free action, the pointman may activate this ability at the start of a combat round. All teammates and allies within line of sight who can hear the pointman's voice (including the pointman himself gain 1 extra half action during this round. This half action may be a standard attack. No character may benefit from this ability more than once per round.



