%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Scientist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

The SGC deals with a variety of situations and races unknown on Earth, these conditions call for the technical and scientific expertise of Earth's greatest minds, and those of her allies. The scientist may begin work with the SGC as a mild-mannered academic, but after a few operations on isolated worlds he quickly picks up the essentials of being an SG team member. A team without a scientist may find itself unable to glean a solution to a technical problem or an explanation for a mysterious event.

\columnbreak

\textbf{Abilities:} The scientist contributes to his team's exploits with the strength of his mind, and a high Intelligence is therefore key. Also, Wisdom supports the analytical skills that let the scientist bring his mind to bear against a problem.


\textbf{Vitality:} d8

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Appraise & Int\\
Balance & Dex\\
Computers & Int\\
Concentration & Wis\\
Craft & Int\\
Cryptography & Int\\
Cultures & Wis\\
Demolitions & Int\\
Diplomacy & Cha\\
Driver & Dex\\
Electronics & Int\\
First Aid & Wis\\
Forgery & Int\\
Hobby & Wis\\
Knowledge & Int\\
Languages & Int\\
Listen & Wis\\
Mechanics & Int\\
Profession & Wis\\
Search & Dex\\
Sense Motive & Wis\\
Spot & Wis\\
Surveillance & Wis\\
Survival & Wis\\
Xeno-Languages & Int\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 8 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}
\gooddefb{}
\poorinit{}
\goodgear{}
\goodres{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Learned, Professor \textsuperscript{*}}
\leveltwo{Ph.D. (1 Skill)}
\levelthree{lmprovise +2}
\levelfour{Research}
\levelfive{lmprovise +3}
\levelsix{Brilliant +1}
\levelseven{lmprovise +4}
\leveleight{Research}
\levelnine{Brilliant +2, lmprovise +5}
\levelten{Know It All 1/Mission}
\leveleleven{lmprovise +6, Ph.D. (2 Skill)}
\leveltwelve{Brilliant +3, Research}
\levelthirteen{lmprovise +7}
\levelfourteen{10-Second Solution}
\levelfifteen{Brilliant +4, lmprovise +8}
\levelsixteen{Research}
\levelseventeen{lmprovise +9}
\leveleighteen{Brilliant +5}
\levelnineteen{lmprovise +10, Ph.D. (3 Skill)}
\leveltwenty{Know It All 2/Mission, Research}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The scientist begins play with the following feats:

Armor Group Proficiency (Light)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Handgun)

\textbf{Professor:} As a free action, the scientist may spend 1 action die to grant the benefits of any basic skill feat he possesses to each other member of his team. The scientist may grant the benefits of any number of basic skill feats to his teammates, up to the number of basic skill feats he possesses, at a cost of 1 action die per feat granted. This effect lasts for the duration of the current scene.

\vspace*{5pt}
\tagline{\textbf{This is the \currentclassname's core ability.}}

\textbf{Learned:} Beginning at 1st level and for each class level gained thereafter, the scientist receives 1 additional skill point which must be spent on a Knowledge skill

The scientist also gains the Scholarly feat. All prerequisites for this feat - including minimum skill ranks - are waived.

\textbf{Ph.D.:} At 2nd level, the scientist may choose 1 lntelligence-based skill. His maximum ranks with this skill increase to his character level + 10 . This skill rank maximum cannot be further increased by feats or other abilities (though it rises naturally as the scientist's character level increases).

At 11th level, the scientist may choose a second lntelligence-based skill to receive this benefit.

At 19th level, the scientist may choose a third lntelligence-based skill to receive this benefit.

\textbf{lmprovise:} The scientist is a master of last minute inspiration and quick technical fixes. At 3rd level, he gains a +2 competence bonus with all repair checks (see the Computers, Electronics, and Mechanics skill descriptions for more information about repair checks). The scientist further gains this bonus with all inspiration checks made to learn the technological solution to a problem (if such a solution exists).

This bonus increases by an additional +1 at 5th level, and for every 2 character levels gained thereafter.

\textbf{Research:} The scientist's work branches out into a variety of fields, allowing him to develop unique specialties. At 4th level, and for every 4 character levels gained thereafter,the scientist may choose one of the following special abilities. Each of these abilities may be chosen multiple times.

\begin{description*}
\item[\hspace{1.5cm}Feat:] The scientist gains one bonus basic or advanced skill feat. He must meet all prerequisites of the feat before choosing it.
\item[\hspace{1.5cm}Inspiration:] Once per session as a free action, the scientist may make one inspiration check without spending an action die.
\item[\hspace{1.5cm}Versatility:] The scientist chooses 2 cross-class skills.These skills become class skills for him. If the scientist uses his versatility class ability to turn Hobby into a class skill for him, then all Hobby focuses are considered to be class skills for him.
\end{description*}

\textbf{Brilliant:} At 6th level, the scientist's Intelligence score rises by 1.

The scientist's lntelligence score rises by an additional 1 at 9th level, and for every 3 character levels gained there-after (to a total rise of 2 at 9th level, 3 at 12th level, 4 at 15th level, and 5 at 18th level).

\textbf{Know It All:} The scientist sometimes displays unusual knowledge of a topic. Far beyond what his comrades thought he knew. At 10th level, once per mission as a free action, the scientist may choose one basic skill feat he already possesses. He immediately gains the Advanced Skill Mastery and Grand Skill Mastery feats linked to this basic skill feat. All prerequisites for these feats -including minimum character level -are waived. The scientist retains these feats until the end of the current mission.These feats are temporary, and may not be used to meet the prerequisites of other feats or the requirements of a prestige class.

At 20th level, the scientist may use this ability up to twice per mission.

\textbf{10-Second Solution:} The team can usually count on the scientist for last minute solutions… that work. At 14th level, once per session, the scientist may designate one Intelligence- or Wisdom-based skill check with which he is considered to automatically roll a natural 20 . This roll is considered a threat and may be activated as a critical success. The scientist must declare that he's using this ability before he makes the roll for the chosen activity.

Further, the designated skill check is accomplished in 1/2 the usual amount of time (rounded down), to a minimum of 1 half action.
