%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Scout}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

With so many operations taking place on worlds with little or no technological infrastructure, the SGC finds itself with a pressing need for operatives with experience in primitive conditions. A team without a scout may find itself unable to adapt, maneuver, or survive if cut off from the Stargate.

\columnbreak

\textbf{Abilities:} The Scout must be able to survive in an alien environment without logistical support. This makes the scout's Wisdom and Constitution scores of paramount importance.

\textbf{Vitality:} d10

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Climb & Str\\
Concentration & Wis\\
Craft & Int\\
Cultures & Wis\\
Driver & Dex\\
First Aid & Dex\\
Gather Information & Cha\\
Handle Animal & Cha\\
Hide & Dex\\
Innuendo & Wis\\
Jump & Str\\
Listen & Wis\\
Move Silently & Dex\\
Search & Int\\
Sport & Str/Dex\\
Spot & Wis\\
Survival & Wis\\
Swim & Str\\
Tumble & Dex\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 6 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\modebab{}
\goodfor{}
\moderef{}
\poorwil{}
\poordefb{}
\goodinit{}
\modegear{}
\moderes{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Stalker, Trailblazer \textsuperscript{*}}
\leveltwo{Rough Living +2}
\levelthree{Bushmaster}
\levelfour{Sneak Attack +1d6}
\levelfive{Bushmaster}
\levelsix{Hunter}
\levelseven{Bushmaster}
\leveleight{Sneak Attack +2d6}
\levelnine{Bushmaster, Hunter}
\levelten{Alert (+2)}
\leveleleven{Bushmaster, Rough Living +4}
\leveltwelve{Hunter, Sneak Attack +3d6}
\levelthirteen{Bushmaster}
\levelfourteen{Overrun}
\levelfifteen{Bushmaster, Hunter}
\levelsixteen{Sneak Attack +4d6}
\levelseventeen{Bushmaster}
\leveleighteen{Hunter}
\levelnineteen{Bushmaster, Rough Living +6}
\leveltwenty{Alert (+4), Sneak Attack +5d6}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The explorer begins play with the following feats:

Armor Group Proficiency (Light)

Armor Group Proficiency (Medium)

Armor Group Proficiency (Heavy)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Hurled)

Weapon Group Proficiency (Handgun)

Weapon Group Proficiency (Rifle)

\textbf{Trailblazer:} The scout's primary responsibility is ensuring that every member of his team survives the hostile environments sometimes encountered beyond the gate. As a free action, the scout may spend 1 action die to grant the benefits of any one terrain feat he already possesses to each member of his team. The scout may grant the benefits of any number of terrain feats to his teammates, up to the number of terrain feats he possesses, at a cost of one action die per feat granted.

This effect lasts for the duration of the current scene. 

\vspace*{5pt}
\tagline{\textbf{This is the \currentclassname's core ability.}}

\textbf{Stalker:} Beginning at 1st level, and for every class level gained thereafter, the scout receives 1 additional skill point which must be spent on the Survival skill.

The scout also gains the Outdoorsman feat. All prerequisites for this feat- including minimum skill ranks - are waived.

\textbf{Rough Living:} The scout's time spent living in the wilds toughens him against cuts and bruises. At 2nd level, he gains a +2 natural armor bonus to his Defense (this bonus stacks with armor and class Defense bonuses, even though armor and class Defense bonuses don't stack with one another). The scout also gains a +2 competence bonus with all saves made against environmental dangers.

At 11th level, both of these bonuses increase to +4.

At 19th level, both of these bonuses increase ro +6.

\textbf{Bushmaster:} At 3rd level, the scout gains 1 bonus basic combat or terrain feat. He must meet all prerequisites for the feat before choosing it.

At 5th level and for every 2 class levels gained thereafter, the scout gains 1 additional basic combat or terrain feat, with the same restrictions.

\textbf{Sneak Attack:} At 4th level, the precision of the scout's blows causes additional damage. The scout gains a +1d6 sneak attack bonus to damage when either flanking a target or attacking a target who is currently denied his Dexterity bonus to Defense (including a target who is flat-footed or immobilized).

This bonus increases by an additional +1d6 at 8th level and for every 4 class levels gained thereafter.

This bonus is only applied to ranged attacks when the target is within 1 range increment. Beyond that, the accuracy needed to hit the target's vitals cannot be managed.

The scout may make a sneak attack with any weapon (or unarmed attack) - even a weapon that deals subdual damage. However, he cannot use a weapon that deals normal damage to inflict subdual damage during a sneak attack,even by accepting the standard -4 circumstance penalty to do so.

Further, the scout's effectiveness with autofire and strafe attack actions is limited when making a sneak attack.

Finally; the scour may not sneak attack targets who are immune to critical hits, who have total concealment, or whose vitals are out of reach.

\textbf{Hunter:} At 6th level, and for every 3 class levels gained thereafter, the scout may choose one of the following special abilities. Unless otherwise specified, each of these abilities may only be chosen once.

\begin{description*}
\item[\hspace{1.5cm}Feat:] The scout gains one bonus advanced skill feat for which the Outdoorsman feat must be a prerequisite. The scout must meet all prerequisites for the feat before choosing it. The scout may choose this special ability more than once, each time gaining one additional advanced skill feat,with the same restrictions.
\item[\hspace{1.5cm}Game Hunter:] The scout is highly skilled at hunting animals, able to drop even largest game with just one ranged shot or melee strike. When the scout attacks a target animal (i.e. any creature with an Intelligence of 2 or lower), his threat range increases by 3 (e.g. a threat range of 19-20 becomes 16- 20).
\item[\hspace{1.5cm}Keen Senses:] The scout's sense of smell is so keen that he may detect opponents purely by their typically undetectable odor. He senses the presence of other people (and animals) within 30 ft. unless they have specifically masked their scent or are scentless. This range increases to 60 ft. if the target is located upwind and drops to 15 ft. if the target is located downwind. Distinctive scents (such as blood, carrion, offal, and perfume) are detected at twice this usual distance.

This ability only informs the scout that someone (or something) is present - it doesn't provide a sense of direction toward the target unless the scout is adjacent to the target (i.e. within 5 feet).

Per the GM's discretion, the scout may also identify familiar odors, such as known foods, his teammates, etc., with the same clarity that most people can identify such things by sight.

Finally the scout ignores visibility penalties while tracking.
\item[\hspace{1.5cm}Man Hunter:] The scout's vast knowledge of the wilds may even be applied when his prey is hiding in an urban setting. He may use his Survival skill when tracking at all times, even when tracking indoors. The scout must possess the Track feat before choosing this ability.
\item[\hspace{1.5cm}Night Vision:] The scout gains the Blindsight 5-ft.Radius feat and can see up to 60 ft. in all but total darkness as if it were daylight. All prerequisites for this feat - including minimum character level - are waived.
\item[\hspace{1.5cm}Silent Rush:] The scout gains the benefits of the Hidden Run feat while operating in any terrain covered by one of his terrain feats. All prerequisites for this feat - including minimum skill ranks and other feats- are waived.
\item[\hspace{1.5cm}Woodcraft:] The scout possesses a huge arsenal of tricks and techniques -for use during outdoor operations. The competence bonuses gained from all terrain feats he possesses increase by an additional +1 (to a total competence bonus of +3). This ability may be chosen a second time, increasing the scout's total competence bonuses by an additional +1 (to a total competence bonus of +4).
\end{description*}

\textbf{Alert:} At 10th level, the scout's Wisdom rises by 2.

At 20th level, the scout's Wisdom rises by an additional 2 (to a total rise of 4).

\textbf{Overrun:} The scout knows that the first few seconds of any fight are often the most critical. At 10th level, once per session as a free action at the start of the first round of combat the scout and each of his teammates and allies within 30 ft gains a modified version of the Great Cleave feat that may be used with unarmed, melee, and ranged attacks. This benefit lasts for a number of rounds equal to each character's Wisdom modifier, but no longer than the scout's Wisdom modifier (minimum 1 round).

This ability may only be used in a terrain covered by one of the scout's terrain feats.



