%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Soldier}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

A mainstay of SG field teams, the soldier is drawn from highly trained and disciplined military forces associated with the Stargate Command. The soldier is the team's backbone during firefights - no other member of an SG team is as expertly trained with combat techniques and strategies. How that training manifests differs from one soldier to another - some are intense martial artists, while others are master marksmen. Without at least one soldier around, the team is likely to find itself outgunned during a serious fight.

\columnbreak

\textbf{Abilities:} Strength, Constitution, and Dexterity are the soldier's most important abilities. They enable superiority in combat, and for a soldier, nothing is more vital.

\textbf{Vitality:} d12

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Climb & Str\\
Concentration & Wis\\
Craft & Int\\
Demolitions & Int\\
Driver & Dex\\
First Aid & Wis\\
Intimidate & Str/Cha\\
Jump & Str\\
Profession & Wis\\
Sport & Str/Dex\\
Spot & Wis\\
Survival & Wis\\
Swim & Str\\
Tumble & Dex\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 4 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\goodbab{}
\modefor{}
\poorref{}
\goodwil{}
\poordefb{}
\goodinit{}
\modegear{}
\poorres{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Bonus Feat, Accurate \textsuperscript{*}}
\leveltwo{Damage Reduction 1/-}
\levelthree{Bonus Feat}
\levelfour{Armor Use +1}
\levelfive{Bonus Feat}
\levelsix{Weapon Specialization}
\levelseven{Bonus Feat}
\leveleight{Armor Use +2}
\levelnine{Bonus Feat, Weapon Specialization}
\levelten{Portable Cover (1/4 Cover)}
\leveleleven{Bonus Feat, Damage Reduction 2/-}
\leveltwelve{Armor Use +3, Weapon Specialization}
\levelthirteen{Bonus Feat}
\levelfourteen{One in a Million}
\levelfifteen{Bonus Feat, Weapon Specialization}
\levelsixteen{Armor Use +4}
\levelseventeen{Bonus Feat}
\leveleighteen{Weapon Specialization}
\levelnineteen{Bonus Feat, Damage Reduction 3/-}
\leveltwenty{Armor Use +5, Portable Cover (1/2 Cover)}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The explorer begins play with the following feats:

Armor Group Proficiency (Light)

Armor Croup Proficiency (Medium)

Armor Group Proficiency (Heavy)

Weapon Group Proficiency (Hurled)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Handgun)

Weapon Group Proficiency (Rifle)

Weapon Group Proficiency (Tactical)

\textbf{Accurate:} Whenever the soldier spends 1 action die to increase an attack check or a Strength- or Constitution-based skill check, 2 dice are added instead of 1 (e.g. a 1st-level soldier's bonus of 1d4 becomes 2d4).

\vspace*{5pt}
\tagline{\textbf{This is the \currentclassname's core ability.}}

\textbf{Bonus Feat:} At 1st level the soldier gains 1 bonus feat from any combat tree (basic, melee, ranged, or unarmed). He must meet all prerequisites for the feat before choosing it.

At 3rd level, and for every 2 class levels gained thereafter, the soldier gains 1 additional bonus combat Feat, with the same restrictions.

\textbf{Damage Reduction:} Starting at 2nd level, the soldier can easily shrug off most minor damage, gaining 1 point of damage reduction.

At 11th level, the soldier's damage reduction increases to 2 points.

At 19th level, the soldier's damage reduction increases to 3 points.

These points follow all the standard rules for damage reduction, and stack with points of damage reduction gained from armor, other class abilities, and other character options.

\textbf{Armor Use:} Starting at 4th level, the soldier's total Defense bonus when wearing armor increases by +1 and the total armor check penalty he suffers from wearing armor is reduced by 1.

At 8th level, and for every 4 class levels gained thereafter, this Defense bonus increases by an additional +1 and the armor check penalty decreases by an additional 1.

This ability cannot reduce the soldier's armor check penalty below 0.

\textbf{Weapon Specialization:} At 6th level, the soldier chooses one weapon category with which he's proficient (e.g."barehanded", "dagger", "grapple", "shotgun", etc.). He is considered to specialize with this weapon category, inflicting 2 additional points of damage with each successfuI hit using any included weapon. lf the soldier's choice is a ranged weapon category, this bonus applies only when the target is within 1 range increment.

At 9th level, and for every 3 class levels gained thereafter, the soldier may specialize with one additional weapon.

\textbf{Portable Cover:} Starting at 10th level, whenever the soldier takes a standard half action attack, he is considered to benefit from one-quarter cover until his next action, even when standing out in the open.

At 20th level this benefit increases to one-half cover.

Cover bonuses do not stack, so the soldier only gains the bonuses offered by the greatest percentage of cover from which he currently benefits (e.g. a 10th-level soldier behind three-quarters over receives no additional benefit from this ability).

\textbf{One in a Million:} At 14th level, once per session, the soldier may designate one attack check, Reflex or Fortitude save, or ability or skill check for which Strength, Constitution, or Dexterity is applied. The soldier is considered to automatically roll a natural 20 with this check. This roll is considered a threat and may be activated as a critical success. The soldier must declare that he's using this ability before he makes the roll for the chosen activity.
