%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Wheelman}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}

The wheelman thrives on high-speed chases and the rush of deadly battles. He is both the team’s vehicle specialist and a trained combatant second only to the soldier class. Without a wheelman, the team might find itself unable to cope when a mission requires breakneck speed and nerves of steel, or a quick getaway.

\columnbreak

\textbf{Abilities:} Dexterity is by far the most important ability for a wheelman, since it is the basis for all vehicle skills, as well as ranged attack rolls. Intelligence is his secondary ability — as a source of extra skill points, many of which are devoted to combat skills.

\textbf{Vitality:} d12

\end{multicols}

\begin{table}[htb]
\rowcolors{1}{white}{stargateblue}
\raggedright
\begin{tabular}{l c}
\textbf{Class Skill} & \textbf{Key Ability}\\

Balance & Dex\\
Boating & Dex\\
Craft & Int\\
Demolitions & Int\\
Disguise & Cha\\
Driver & Dex\\
Escape Artist	& Dex\\
Handle Animal &Cha\\
Intimidate & Str/Cha\\
Jump & Str\\
Mechanics & Int\\
Open Lock & Dex\\
Perform & Cha\\
Pilot & Dex\\
Profession & Wis\\
Sport & Str/Dex\\
Spot & Wis\\
Surveillance & Wis\\
Survival & Wis\\
Swim & Str\\

\multicolumn{2}{l}{\cellcolor{white}}\\
\multicolumn{2}{l}{\cellcolor{white}\textbf{Skills/Level:} 6 + Intelligence Bonus}\\
\end{tabular}
\end{table}

\pagebreak

\goodbab{}
\poorfor{}
\goodref{}
\poorwil{}
\modedefb{}
\modeinit{}
\modegear{}
\moderes{}

\begin{table}[ht]
\caption{The \currentclassname}
\begin{adjustbox}{width=\columnwidth,center}
\rowcolors{1}{white}{stargateblue}
\begin{tabular}{l c c c c c c c c l}

\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Defense} & \textbf{Initiative} & \textbf{Gear Picks} & \textbf{Res Pts} & \textbf{Special}\\
\levelone{Starting Feats, Daredevil, Custom Ride (4 RP) \textsuperscript{*}, Lucky \textsuperscript{*}}
\leveltwo{Kick Start 1/Session}
\levelthree{Bonus Feat}
\levelfour{Familiarity +1, Custom Ride (5 RP) \textsuperscript{*}}
\levelfive{Bonus Feat}
\levelsix{Elbow Grease +2}
\levelseven{Bonus Feat}
\leveleight{Familiarity +2, Custom Ride (6 RP) \textsuperscript{*}}
\levelnine{Bonus Feat, Elbow Grease +4}
\levelten{Soup Her Up (25\%)}
\leveleleven{Bonus Feat, Kick Start 2/Session}
\leveltwelve{Elbow Grease +6, Familiarity +3, Custom Ride (7 RP) \textsuperscript{*}}
\levelthirteen{Bonus Feat}
\levelfourteen{“That’s Impossible!”}
\levelfifteen{Bonus Feat, Elbow Grease +8}
\levelsixteen{Familiarity +4, Custom Ride (8 RP) \textsuperscript{*}}
\levelseventeen{Bonus Feat}
\leveleighteen{Elbow Grease +10}
\levelnineteen{Bonus Feat, Kick Start 3/Session}
\leveltwenty{Familiarity +5, Soup Her Up (50\%), Custom Ride (9 RP) \textsuperscript{*}}

\multicolumn{10}{l}{\cellcolor{white}}\\
\multicolumn{10}{l}{\cellcolor{white}\textbf{\textsuperscript{*} Core Ability} - A character only ever gains the core abilities of the first base dass and the first prestige class he chooses.}\\
\end{tabular}
\end{adjustbox}
\end{table}

\classfeatures

\textbf{Starting Feats:} The wheelman begins play with the following feats:

Armor Proficiency (Light)

Armor Proficiency (Medium)

Weapon Group Proficiency (Handgun)

Weapon Group Proficiency (Melee)

Weapon Group Proficiency (Rifle)

Weapon Group Proficiency (Tactical)

\textbf{Custom Ride:} At the start of each mission, the wheelman gains 4 resource points with which he may requisition a team vehicle, vehicles, or vehicular improvements. This bonus increases by an additional 1 resource point at 4th level, and for every 4 class levels gained thereafter.

The wheelman may spend these resource points independently or together with his regular allotment, or may pool them with other team members’ resource points for more expensive vehicles and improvements. These bonus resource points may only be used to requisition vehicles and vehicular improvements.

When multi-classing, these resource points are only received when the character gains a level in his wheelman class.

\vspace*{5pt}
\tagline{\textbf{This is one of the \currentclassname's two core ability.}}

\textbf{Lucky:} Whenever the wheelman spends 1 action die to increase a vehicle-related skill check (such as Mechanics or Driver), 2 dice are added instead of 1 (e.g. a 1st-level wheelman’s bonus of 1d4 becomes 2d4). In addition, the Gamemaster must spend 1 extra action die to activate each of the wheelman’s errors with a vehicle-related skill check as a critical failure.

\vspace*{5pt}
\tagline{\textbf{This is one of the \currentclassname's two core ability.}}

\textbf{Daredevil:} During a vehicular scene, the wheelman may choose daredevil-only maneuvers and weather certain other maneuvers more easily.

\textbf{Kick Start:} Starting at 2nd level, once per session, the wheelman may change a failed Mechanics skill check to a success by giving the target device a whack in frustration.

At 11th level, the wheelman may use this ability up to twice per session, and at 19th level, the wheelman may use this ability up to three times per session.

\textbf{Bonus Feat:} At 3rd level, the wheelman gains the Speed Demon feat or 1 bonus chase feat. He must meet all prerequisites for the feat before choosing it.

At 5th level and for every 2 class levels gained thereafter, the wheelman gains 1 additional bonus chase feat or an Advanced Skill feat with Speed Demon as a prerequisite, with the same restrictions.

\textbf{Familiarity:} Starting at 4th level, at the start of each mission, the wheelman may designate any 1 vehicle that he’s already operated in play for at least 20 days minus a number of days equal to his Wisdom modifier as ‘familiar’. The wheelman may designate his custom ride as familiar if he wishes.

For the duration of the current mission, the wheelman gains a +1 competence bonus with Boating, Driver, Mechanics, Pilot, and maneuver checks made using the vehicle with which he’s ‘familiar’. He also gains this bonus with attack checks made firing the vehicle’s weapons.

At 8th level and for every 4 class levels gained thereafter, each of these bonuses increase by an additional +1.

\textbf{Elbow Grease:} Starting at 6th level, the wheelman gains a +2 competence bonus with Mechanics repair checks, whether the repairs are to a vehicle or another item.

At 9th level and for every 3 class levels gained thereafter, this bonus increases by an additional +2.

\textbf{Soup Her Up:} Starting at 10th level, at the start of each mission, the speed, MPH, Defense, wound point maximum, hardness, and options of any vehicle with which the wheelman is familiar are increased to 125\% standard (rounded up). If the vehicle’s handling modifier is positive, this bonus applies to it as well; otherwise, the vehicle’s handling modifier is reduced to 75\% standard (rounded down).

At 20th level, each of these bonuses increases to 50\%.

\textbf{“That’s Impossible!”:} Starting at 14th level, once per game session when driving a vehicle, the wheelman may force it to utterly defy physics for one maneuver. For example, the wheelman might fly an X-301 Interceptor through a seemingly annihilative gravity well, vertically loop a helicopter with a two-bladed rotor, leap a motorcycle over a train just as a flatcar goes past, balance an 18-wheeler on half its wheels, etc.

During a vehicular scene, the wheelman may ignore the negative penalties of any maneuve. At all other times, the Gamemaster determines this ability’s effects, based on requests made by the wheelman and the conditions at hand.


